\documentclass[proposal.tex]{subfiles}

\begin{document}
    
\section{Motivation}

Internet denizens have long found ways to have vibrant communications about a wide variety of content. In the past, more websites supported these conversations through comment sections, but many have shuttered their comments in recent years. Instead, the avenues of discourse have become social media sites such as Facebook, Reddit, and bulletin board style forums, decoupling the conversation from the content itself.

Tying comments to social media posts rather than the content has the effect of fragmenting the conversation and diluting the information available to viewers. Comment Anywhere will bring the discussion back to where the content is at, traveling with the content as it is shared across platforms and accessible to all users of Comment Anywhere. By being able to open Comment Anywhere and immediately jump into a discussion about the content they are viewing, our users will be able to find information from outside their social network and contribute their own relevant information that will stick to that content wherever it goes.

At their best, comments are a forum for lively debate of the issues reported on or expressed in a piece, as well as a source for personal experiences and further information related to the story. The idea that information should be freely accessible runs deep within the ideology of the internet.
\\\\
Comment Anywhere will make conversation available and accessible for all content, increasing the public's access to information, and thereby improving the internet.

\end{document}