\documentclass[proposal.tex]{subfiles}

\begin{document}
    
\section{Objectives}

\subsection{Browser Extensions}

Users will interact with Comment Anywhere through browser extensions that can be downloaded and installed on popular browsers, such as Google Chrome and Mozilla Firefox. These extensions will comprise the majority of the "front end" component of the software. 

\subsection{Human Moderation}

Comments will be subject to human moderation through several means.

\begin{enumerate}
    \item User Ratings - Similar to Likes or Upvotes, users should be able to rate the relevancy of a comment. Higher rated comments rise to the top.
    \item User Reports - Comments that are off topic, violate community guidelines or standards, or contain offensive material can be reported for manual moderation.
    \item Moderator Review - Designated volunteer moderators will evaluate comments that are flagged by users and by the automoderation system and determine appropriate actions to take based on commenting rules.
\end{enumerate}

\subsection{Automated Moderation}

Human moderation has high overhead and it is infeasible to have a human to review every single comment that is posted. To reduce costs and catch more rule-breaking comments, comments will be subject to automatic evaluation at the time of submission. Sentiment Analysis, keyword searches, and machine learning can all be applied to analyze comments upon submission to find rule breaking behavior and take direct action or flag the comment for human review.

\subsection{Backend Services}

Comment Anywhere will rely on a number of backend services including:

\begin{itemize}
    \item Comment Database and API
    \item Comment Analysis and Moderation
    \item Comment Delivery
    \item User Authentication
    \item Security, Password encryption
    \item Metrics
    \item User Information
    \item Moderation and Administration Services
\end{itemize}

\end{document}